Rates of true polar wander in convecting planets

### 2014-07-02 tpw_rate.tex
Text in rotational dynamics

\section{Rates of true polar wander}

@@

Without loss of generality we may choose the coordinate system such that $\phi=0$:
\begin{equation}
\dot{\theta} = - \frac{1}{2 \varepsilon \tau}\sin{2 \theta} \frac{(\lambda_3-\lambda_1)}{I_0}
\end{equation}

These equations are a version of what has been called the ``Milankovitch theorem'' \citep{munk1960rotation}.  
Written this way, it is clear that the important quantities are $\theta$ and the differences between the eigenvalues of the convective moment $\bf E$.
We may rewrite this in terms of the nondimensional numbers defined above, where $\varepsilon \sim \mathrm{Fr}$ and $\tau \sim \eta / \rho g R \sim \frac{R^2}{\kappa} \Gamma/\mathrm{Ra}$.

\begin{equation}
\dot{\theta} \sim - \frac{\mathrm{Ra}}{\Gamma \mathrm{Fr}} \sin{2 \theta} \frac{(\lambda_3-\lambda_1)}{I_0}
\end{equation}

Thus it remains to derive estimates for these.

>>>>

\section{Rotational dynamics}

@@

Without loss of generality we may choose the coordinate system such that $\phi=0$:
\begin{equation}
\dot{\theta} = - \frac{1}{2 \varepsilon \tau}\sin{2 \theta} \frac{(\lambda_3-\lambda_1)}{I_0}
\label{simple_milankovitch}
\end{equation}

These equations are a version of what has been called the ``Milankovitch theorem'' \citep{munk1960rotation}.  
Written this way, it is clear that the important quantities are $\theta$ and the differences between the eigenvalues of the convective moment $\bf E$.
It is useful to define a nondimensional eigenvalue difference (or ``eigengap'') $\Lambda_{ij} = (\lambda_i - \lambda_j)/I_0$.  
With this we may rewrite this in terms of the nondimensional numbers defined above, where 
$\varepsilon \sim \mathrm{Fr}$ and $\tau \sim \eta / \rho g R = \frac{R^2}{\kappa} \Gamma/\mathrm{Ra}$.

\begin{equation}
\frac{\kappa}{R^2} \; \dot{\theta} \sim - \frac{\mathrm{Ra}}{\Gamma \mathrm{Fr}} \Lambda_{31} \sin{2 \theta}
\end{equation}

At this point we do not have estimates for the characteristic magnitudes of $\Lambda_{ij}$ or $\theta$, both of which are crucial for estimating characteristic rates of TPW.
They represent, respectively, the size of convective anomalies in the moment of inertia tensor and the angular mismatch between where the 
convective moment
